Realistically Interesting Domains for Probabilistic Planners

### 2014-04-07 FinalPaper/paper.tex
adjusted ff-replan

\section{Domains}

% TODO we only look at IPPC-11 domains
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

@@

\subsubsection{Navigation}

@@

\subsubsection{Traffic}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.

@@

\subsection{Elevators}

In the elevators domain there are a number of elevators delivering passengers
to either the top or bottom floor. Potential passengers arrive at any floor at
a certain rate (depending on which floor). The elevators can only move in the
direction it is indicating, so passengers know whether to board or not. The
goal of the elevators is to transport as many as possible passengers to their
destinations.

\subsection{SysAdmin}

The SysAdmin domain describes a network of connected servers. Each server has
a probability that it shuts down, and if is not running, it has a probability
to reboot. The probability that a server shuts down depends on the number of
running connected servers.

@@

\subsection{Real-World Domain Evaluation}

\subsubsection{Navigation}

@@

\subsubsection{Traffic}

The traffic domain describes a crossroad with traffic lights, modelled as
cells. Either the north to south road has a green light, the west to east road
or all lights are red. The model uses a finite state machine that handles the
lights so that the lights are never green at the same time. This would be the
only dangerous situation on the crossroad. The difficulty in this domain is
the number of states, which grows exponentially with the number of cells.
Besides that it is an uninteresting probabilistic problem because it does
not satisfy the probabilistic interesting test.

\subsubsection{Elevators}

@@

In sections above we have described the GOURMAND planner and FF-Replan as two
probabilistic planners of the IPPC competition.
RFF~\cite{teichteil2010incremental} is an offline planner that generates a
policy: for each reachable state it determines a plan to the goal. Like
FF-Replan it uses determinization and FF\. FF returns an initial plan from the
initial state to a goal state. For each state in the plan the successor states
are added to the structure, after which Monte-Carlo sampling is used. States
where the probability that they're reached is too low (below a threshold) are
removed. The successor states are used as initial states in the next step. If
FF fails to find a plan to the goal from this new state, the state is removed
from the structure too. Results showed that RFF outperformed other competitors.
A higher threshold means that RFF will generate more policies that are prone to
replanning.

>>>>

\section{Domains}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

@@

\subsubsection{Navigation domain}

@@

\subsubsection{Traffic domain}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.

@@

@@

\subsection{Real-World evaluation}

\subsubsection{Navigation domain}

@@

@@

\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
